---
title: "Homework 1"
author: "Yuki Joyama"
date: "2023-09-23"
output: 
  html_document: default
  pdf_document: default
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE) 
knitr::opts_chunk$set(fig.width=5, fig.height=2) 
```

# Problem 1

a)  Qualitative, ordinal
b)  Qualitative, binary
c)  Qualitative, ordinal
d)  Quantitative, continuous
e)  Quantitative, discrete

# Problem 2

The depression scores for 14 individuals with a recent bike crash history (I will define this as group A):  
45, 39, 25, 47, 49, 5, 70, 99, 74, 37, 99, 35, 8, 59

a)  Descriptive summaries 
```{r descriptive, cache = T, echo=F}
# data input
depression_score <- c(45, 39, 25, 47, 49, 5, 70, 99, 74, 37, 99, 35, 8, 59)
# calculate descriptive summaries
range_score <- max(depression_score) - min(depression_score)
```
Mean: $\sum_{i=1}^{14}\frac{x_i}{14}$ = `r round(mean(depression_score), digits = 2)`\
Median: $(45+47)/2$ = `r round(median(depression_score), digits = 2)`\
Range: $99-5$ = `r round(range_score, digits = 2)`\
SD: $\sqrt{\frac{1}{14-1} \sum_{i=1}^{14} (x_i - \overline{x})^2}$ = `r round(sd(depression_score), digits = 2)`

b)  Box plot of the depression scores of group A
```{r histogram, eval=F, echo=F}
hist(depression_score)
```

The box plot and histogram (plot not shown) indicate right-skewed, unimodal distribution.

``` {r plot, cache = T, echo = F}
library(ggplot2)
# create a box plot 
ggplot() +
  geom_boxplot(aes(y = depression_score)) +
  scale_x_discrete() +
  labs(y = "The depression score") +
  coord_flip()
```

The depression scores for 13 individuals with a recent car crash history (I will define this as group B):  
67, 50, 85, 43, 64, 35, 47, 97, 58, 58, 10, 56, 50

```{r additional, cache = T, echo=F}
# data input
depression_score_1 <- data.frame(score = depression_score, group = "A")
depression_score_2 <- c(67, 50, 85, 43, 64, 35, 47, 97, 58, 58, 10, 56, 50) 
depression_score_2 <- data.frame(score = depression_score_2, group = "B")
df <- rbind(depression_score_1, depression_score_2)
```

a) Side-by-side box plot of the depression scores stratified by type of accident 

``` {r newplot, cache = T, echo = F}
library(ggplot2)
# create a box plot 
ggplot(df, aes(x = group, y = score)) + 
  geom_boxplot() +
  labs(x = "Group",y = "The depression score") +
  coord_flip()
```

b) Based on the box plot and histogram (plot not shown), group A appears to have right-skewed, unimodal distribution while group B has left-skewed, unimodal distribution.
This is also supported by the fact mean > median in group A and mean < median in group B.

```{r histogram2, echo=F, eval=F}
hist(depression_score_2$score)
```

c) Judging from the box plot, group A appears to have a lower typical depression score. 

# Problem 3 
Tossing one fair 12-sided die.

a) event A: an even number appears  
Let $\Omega$ = {1, 2, ..., 12}  
Let A = {2, 4, 6, 8, 10, 12}, $A \subset \Omega$  
P(A) = $\frac{6}{12}$ = $\frac{1}{2}$  

b) event B: number 10 appears
Let $\Omega$ = {1, 2, ..., 12}  
Let B = {10}, $A \subset \Omega$  
P(B) = $\frac{1}{12}$

c) $P(B \cup A)= P(A) + P(B) - P(B \cap A)$  
$P(B \cap A)$ is the probability of number 10 appears (which is also an even number), so $P(B \cap A) = \frac{1}{12}$  
Therefore, 
$P(B \cup A)= P(A) + P(B) - P(B \cap A)=\frac{1}{2}+\frac{1}{12}-\frac{1}{12}=\frac{1}{2}$

d) If event A and event B are independent, $P(A \cap B)$ should be equal to $P(A) P(B)$.  
Now, given $P(A) P(B)=\frac{1}{2}\times\frac{1}{12}=\frac{1}{24}\neq P(A \cap B)$, we can say that these two events are not independent.

# Problem 4

Let A be having dementia and B be having positive CT scan findings.  
5% of 75+ year-old women have dementia so $P(A)=0.05$   
Among women with dementia, 80% have positive CT scan findings so $P(B|A)=\frac{P(B\cap A)}{P(A)}=0.8$  
Given $P(A)=0.05$, $P(A\cap B)=0.04$  
10% showed a positive CT scan findings among women who don't have dementia, and this gives $P(B|\bar{A})=\frac{P(B\cap \bar{A})}{P(\bar{A})}=0.1$   
Given $P(\bar{A})=1-0.05=0.95$, $P(B\cap \bar{A})=0.095$  
Now, $P(B)=P(A\cap B)+P(\bar{A} \cap B)=0.04+0.095=0.135$  
Therefore, the probability of a woman with a positive CT scan findings to have dementia is $P(A|B)=\frac{P(A\cap B)}{P(B)}=\frac{0.04}{0.135}=0.30$  

The answer to this question would be 30%.




