---
title: "Homework 1"
author: "Yuki Joyama"
date: "2023-09-23"
output: 
  html_document: default
  pdf_document: default
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE) 
```

## Problem 1

a)  Qualitative, ordinal
b)  Qualitative, binary
c)  Qualitative, ordinal
d)  Quantitative, continuous
e)  Quantitative, discrete

## Problem 2

a)  Descriptive summaries of the depression scores for 14 individuals in a study

```{r descriptive, cache = T}
# data input
depression_score <- c(45, 39, 25, 47, 49, 5, 70, 99, 74, 37, 99, 35, 8, 59)
# calculate descriptive summaries
range_score <- max(depression_score) - min(depression_score)
```

Mean: `r round(mean(depression_score), digits = 2)`\
Median: `r round(median(depression_score), digits = 2)`\
Range: `r round(range_score, digits = 2)`\
SD: `r round(sd(depression_score), digits = 2)`

b)  Box plot of the depression scores of 14 individuals

``` {r plot, cache = T}
library(ggplot2)
# create a box plot 
ggplot() +
  geom_boxplot(aes(y = depression_score)) +
  scale_x_discrete() +
  labs(title = "The depression scores of 14 individuals", 
       y = "The depression score") +
  coord_flip()
```






