---
title: "Simple document"
author: "Jeff"
date: "2023-09-12"
output: 
  html_document: 
    toc: true
    toc_float: true
    code_folding: hide
---

I'm an R Markdown document! 

```{r, echo=F, message=F}
library(tidyverse)
```


# Section 1 First code chunk

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2 Make a plot

This code is borrowed from last lecture; it creates a dataframe for plotting

```{r}
plot_df = tibble(
  x = rnorm(1000, sd = .5),
  y = 1 + 2 * x + rnorm(1000)
)
```

Next up is a histogram of the `x` variable in `plot_df`.

```{r}
ggplot(plot_df, aes(x = x)) + geom_histogram()
```

# Section 3 Learning assessment

This code chunk should creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then, produce a histogram of the absolute value variable just created. Add an inline summary giving the median value rounded to two decimal places. 

```{r learning_assessment_1}
library(tidyverse)

la_df = tibble(
  norm_samp = rnorm(500, mean = 1),
  norm_samp_pos = norm_samp > 0,
  abs_norm_samp = abs(norm_samp)
)

ggplot(la_df, aes(x = abs_norm_samp)) + geom_histogram()

median_samp = median(pull(la_df, norm_samp))
```

The median of the variable containing absolute values is 
`r round(median_samp, digits = 2)`.

# Section 4 Text formatting examples

Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell

